Assessing the Population-Level Conservation Effects of Marine Protected Areas

### 2020-12-03 documents/referee-replies.Rmd

Thank you, we are glad to hear the reviewer feels this is an important contribution.

@@

*My main concerns on reading the paper are that the methods and results are not clearly enough described.*

Thank you for pointing this out, we have reorganized and clarified our methods and results.

*1) Although the parameterisation of the simulation model is provided the equations should be included in supplementary. I did visit the github site and the simulator but neither allowed me to find formulations easily. So first off the simulation model needs to be explained in detail in supp methods including equations.*

Thank you for pointing out the lack of sufficient detail on the equations for the simulation model. We have restructured the SI so that the simulation model equations are front and center (SI Section 2), and clarified our explanations of the equations. We have also expanded our description of the simulation model in the Methods section of the main text. We hope this clarifies the structure behind the simulation model.

@@

*2) On a related note I didn't come away with a clear sense of the scenarios used to simulate the potential fish outcomes. For example I have no clear sense how you have simulated spatial patterns of fishing intensity.*

We apologize for the confusion in the simulation scenarios. Given the wide array of scenarios employed, and the word constraints of the paper, we unfortunately could not include a thorough description of every scenario in the main text. We have however included a clearer summary of the simulation in the methods section, highlighting among other key attributes the ways in which we simulate spatial patterns of fishing intensity, which as Reviewer #2 has noted is a critical variable to consider.

@@

*Similarly, it was not clear to me how you decide which model scenarios are most plausible when conditioning on observed response ratios. Yet conveying the ways in which observed RR could be derived would be useful. There is some discussion of this but not enough to detail. I believe that a good part of the discussion could be removed to make way for this.*

We have expanded our description of the simulation model in an effort to explain this more clearly, and in particular expanded our matching process to address this comment (end of the Simulation Model Methods section). Our Channel Islands simulations were designed to match the genera of species observed in the Channel Islands, our best sense of the exploitation history of those species, and the potential size of the MPAs for those species. For example, we know that all of the finfish species in this analysis are part of populations that span at least the range of the Channel Islands. Since the Channel Islands MPAs make up roughly 20% of the Islands, we know that the MPAs are likely to be no more than 20% of a species range, which we incorporate into the simulations.

@@

*I loved the open data/code approach to this paper, it goes the extra mile by having an online application. I had fun exploring that thanks.*

You are welcome, we are glad it helped.

*The simulation model represents on its own a very complete synthesis of the fish biomass MPA modeling literature, and includes most of the processes and their variants, that have been shown over the past 20 years to affect MPA outcomes.*

We are glad you found the simulation model sufficiently comprehensive.

@@

*There are some minor comments/edits/clarifications below, but my main questions are about the ‘difference-in-difference model’, which seems to be a type of GLMM. I haven’t heard the term before, so I think it needs a bit more explanation. You might want to move some of the explanation from the SI which was really clear, over to the main text.*

We have moved some of the methods from the SI as suggested, which we hope clarifies the connection between difference-in-difference and BACI. We use the term difference-in-difference to tie our results more clearly to the causal inference literature in econometrics. WE have also clarified that use use a GLMM-style model (we refer to it as a hierarchichal generalized linear model since the term mixed effects doesn't quite apply in a Bayesian context) model to account for the spatial nature of our data.

@@

*After reading just the main text I was left with a few questions about the DiD: how the years were binned (and why those bins)? The year ‘bins’ are in the table and figure 4, but in the methods it says there was a just a pre and post MPA time-period.*

Thank you for pointing this out. We have clarified the pre and post time period discussion in the Difference-in-Difference section of our Methods. We chose to bin the results for visual clarity. At the risk of further expanding the already extensive supplementary materials, we have also included a version with a binwidth of 1 (i.e. no binning) to make clear that our results are not sensitive to the choice of binwidth (Fig.S23)

@@

This is a very good point. We include hierarchical terms for each site in the data, clustered by the specific island in the Channel Islands a specific site was located at. This serves to control for any intrinsic traits of the MPA sites themselves, e.g. if MPA sites were preferentially placed on better habitat than "control" sites. The site-specific intercept then represents the mean total biomass density of non-targeted species pre-MPA, conditional on the other covariates in the model.

Our reasoning for not including a specific interaction term for site, whether that site is an eventual MPA, and whether the MPA is in place in a given year, is that this would muddy the interpretation of our key variable of interest; namely the difference in mean total biomass density of targeted finfish throughout the Islands. Adding in a term representing the presence of an active MPA at a site would effectively mean that the our main coefficient of interest, the interaction of the targeted dummy variable with the year blocks, would represent the mean effect of the MPAs on mean total biomass density of targeted finfish controlling for any effect that those MPAs had inside the MPAs.

*If it is included, then the predictions for total density should be post-stratified by total area of MPAs in the seascape?*

This is correct. It was quite buried in the SI, but we do weight the MPA and non-MPA sites according to the total area of MPAs in the seascape, since as the referee points out the sampling regime is not random. We note this weighting in our Methods section now. Otherwise, if the MPAs caused an increase of 50% inside, and 0% outside, given that the PISCO sampling regime has roughly equal sampling inside and outside MPAs, the model would estimate a net effect of 25%, even though MPAs in fact make up roughly 20% of the area.

We also include an unweighted version of our results, to demonstrate that our results are not sensitive to this weighting choice (Fig.S22).

@@

*The supplemental materials are very extensive because they include exploration of multiple different model formulations both models, and also a simulation study testing the difference in difference approach. I think you could cut them down a bit if they wanted, and save some of this for more complete exploration in another paper? I think most readers will never get this far, so it seems a bit of a waste to have all this interesting information in a supplemental. The parts I found most in the SI useful for this particular study were the explanation of the DiD, the simulation study and the documentation of the simulation model.*

Thank you for this point. We reorganized the supplemental materials for ease of reading. However, we have not removed sections at this time. Each of the analyses included in the SI (beyond that basic explanations of the methods) were a result of a question that we received from prior reviewers or peers. As such, we feel that it is better to include these in there for the odd person that really wants to see the results via synthetic controls. Given that the referees primary concern here was our not wasting useful analyses (which we appreciate!), and that we do not intent do dive further into the empirics of this particular question in the Channel Islands at this time, we have elected to go with the conservative approach of a perhaps excessively thorough SI.

@@

Minor comments

*Introduction reads nicely. One comment: it might be worth stating that modeling studies are generally predicting population level effects, but empirical studies are measuring local effects. So another great example of a modeling-empirical disconnect. You’ve set a high expectation in the reader’s mind that you are going to fill this gap, which is then met through the novel combination of simulation and statistical modeling.*

Thank you for this excellent suggestion that we have sought to reflect in our Introduction.

*The references are pretty focused on California, and there is certainly a lot of great MPA literature from that part of the world, but perhaps you could expand the geography a bit to make the relevance to international readers clear? See suggestions below.*

Thank you for pointing this out. We only see one suggested reference (@krueck2017), which we have incorporated. We have also cited @fulton2015 in order to link our more more explicitly to the broader literature on MPA simulation model.

@@

*81: thanks for sharing the code. Note doing that does invalidate your double blind.*

We are glad you found it helpful. We did consider this, and decided that the extra effort needed to blind the code itself was not worthwhile. An interesting challenge for journals seeking to do double blind reviews to consider; it's hard to post code that is both open and reproducible and anonymous!

@@

*89: Nils Kruek did a similar thing in his paper, it might be worth reading and relevant citing:https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.2000537*

Thank you for pointing this out, we have included this citation, as well as @fulton2015, to place are results more clearly into a broader literature of MPA simulation.

@@

*Eqn 1: Don’t the gamma shape and scale depend on its mean? So maybe more correct to write this as: Expectation(d) = exp(beta….) and then say observations were sampled from a gamma, where the dispersion parameter was free/estimated.*

Thank you for the suggestion, in keeping with the likelihood notation here, we have kept the shape (dispersion) parameter in the equation, since the Gamma likelihood does depend on it, but you are right that the scale is a transformation of the mean and the shape and so should be (and has been) omitted.

*It could be helpful to show an equation for the net DiD outcome (as explained at A.3). I think its something like: (D[post, fished]-D[pre, fished]) – (D[post, unfished]-D[pre, unfished])*

We agree this would help readers understand the model and have included this suggestion on in our Methods section.

@@

*Was temporal autocorrelation was dealt with/checked for?*

This is a good question. We considered treating the year effects as hierarchichal terms, which would help account for the autocorrelated nature of observations over time. We elected not to, as doing so would negate their benefits as an identification strategy, controlling for unobserved variables that are correlated with with the timing of MPA placement with the total biomass densities of targeted finfish. As discussed in @larsen2019, treating our year terms as hierarchical (or random effects in the context of that paper) means that we assume that the error distribution of the year terms is uncorrelated with the treatment, meaning that the difference-in-difference no longer acts to remove omitted variable bias, which is its main purpose here.

@@

*Fig 4: indicate pre-MPA period.*

We have clarified that all the year bins are post-MPA, since the MPAs went in place in 2003, in the figure caption. We worry that given the large amount going on in Figure 4 already adding another shaded area might be confusing. The "pre" MPA period is effectively reflected by the intercept term and its relevant interactions.

*189: I don’t think it is overlooked. E.g. see work done on the Great Barrier Reef, where quota management was coordinated with a major MPA rezonining in 2004. Papers by Little in this journal (2009 “Complementarity of No-Take Marine Reserves and Individual Transferable Catch Quotas for Managing the Line Fishery of the Great Barrier Reef”) and Hopf in Current Biology (2016 “Synergistic Effects of Marine Reserves and Harvest Controls on the Abundance and Catch Dynamics of a Coral Reef Fishery”)*

Thank you for pointing this out, and have rephrased this section accordingly to reflect that this is something that stakeholders should be aware of, as demonstrated in Little et al. 2009.

@@

*225: I don’t think this simulation study was reported in the methods and results, but should be, or reference given to appendix?*

We believe there is some confusion, this is the same simulation model as presented in the methods and used elsewhere in the paper. This clearly was not evident in the text though, we have clarified that this is the Simulation Model section of the Methods.

@@

*228: this paragraph belongs in results.*

We have moved this section to the results.

*Discussion: How would poaching in MPAs affect the interpretation of the difference-in-difference model?*

Interesting question. What evidence we have is that poaching is of limited concern in the Channel Islands (but clear can be a major issue in many MPAs). However, the presence of poaching should not bias the estimates of the DiD model in any way: if poaching were severe enough so as to render the MPAs completely ineffective, then in theory a DiD model such as the one implemented here would simply estimate that the MPA had no effect, as their would be no difference in the conditional biomass densities of targeted and non-targeted species.

However, poaching might certainly influence stakeholder interpretation of the results. If poaching is rampant but stakeholders are largely unaware of it, a model like this might estimate the the MPAs had no effect (which in that case they might not). Stakeholders might then interpret that as a problem of MPA design, a misunderstanding of the movement dynamics or fishing pressure in the fishery, or any other number of variables, when in fact the problem was simply that the MPA was not actually acting as an MPA.
